\subsubsection{YAML Element: <scm moniker>.scan-agent.allowed-agent-tags}\label{sec:yaml-scan-agent-allowed-agent-tags}
A list of scan agent tags that are handled by the \cxoneflow service.  The agent tags come from
\cxone project tags using the \texttt{<resolver-tag-key>:<agent tag>} format.  

\subsubsection{YAML Element: <scm moniker>.scan-agent.capture-resolver-logs}\label{sec:yaml-scan-agent-capture-resolver-logs}
If set to True, any logs emitted by the scan agent are transported back to the \cxoneflow server and
emitted in the \cxoneflow logs.  This can be used to troubleshoot issues encountered by scan agents.

\subsubsection{YAML Element: <scm moniker>.scan-agent.default-agent-tag}\label{sec:yaml-scan-agent-default-agent-tag}
An agent tag found in the list of tags configured in \texttt{allowed-agent-tags}.  If provided,
any \cxone project that does not have an agent tag (assigned with the format \texttt{<resolver-tag-key>:<agent tag>})
will direct a scan to Scan Agents with this tag.

\subsubsection{YAML Element: <scm moniker>.scan-agent.private-key}\label{sec:yaml-scan-agent-private-key}
The value specifies a file name found under the path defined by \texttt{secret-root-path}
containing an unencrypted RSA or elliptic curve private key.  The associated public key will be distributed to
Scan Agents.

\subsubsection{YAML Element: <scm moniker>.scan-agent.resolver-tag-key}\label{sec:yaml-scan-agent-resolver-tag-key}
The \cxone project tag key value used to find the scan agent tag that should be used for a delegated scan.
This is described in more detail in Section \ref{sec:scan-agents}.

\subsubsection{<scm moniker>.scan-agent.scan-retries}\label{sec:scan-agent-scan-retries}
The number of times a request for a delegated scan will be retried after the initial request if no Scan Agent handles the scan.
Any scan request not handled by a Scan Agent before the \intlink{sec:scan-agent-scan-timeout-seconds}{scan-timeout-seconds} setting 
will be evaluated for resubmission.  If the number of retries exceeds this amount, the scan will be returned in a failed state.

\subsubsection{<scm moniker>.scan-agent.scan-timeout-seconds}\label{sec:scan-agent-scan-timeout-seconds}
The number of seconds before a scan request is not selected by a Scan Agent before it times out.  When the scan
request times out, it may be resubmitted or aborted as a failed scan.
