\subsubsection{YAML Element: <scm moniker>.connection}\label{sec:yaml-moniker-connection}
A block element where the child elements define the SCM connection parameters for this service definition.

\subsubsection{YAML Element: <scm moniker>.cxone}\label{sec:yaml-moniker-cxone}
A block element where the child elements define the connection configuration for the \cxone API. 

\subsubsection{YAML Element: <scm moniker>.feedback}\label{sec:yaml-moniker-feedback}
A block element where the child elements define the configuration for feedback workflows. 

\subsubsection{YAML Element: <scm moniker>.kickoff}\label{sec:yaml-moniker-kickoff}
A block element where the child elements define the configuration for kickoff workflows. 

\subsubsection{YAML Element: <scm moniker>.project-groups}\label{sec:yaml-moniker-project-groups}
A block element where the child elements define the configuration for automatic project group assignment. 

\subsubsection{YAML Element: <scm moniker>.project-naming}\label{sec:yaml-moniker-project-naming}
A block element where the child elements define the configuration for dynamic project naming. 

\subsubsection{YAML Element: <scm moniker>.resolver}\label{sec:yaml-moniker-resolver}
A block element where the child elements define the configuration for support of resolver agents. 

\subsubsection{YAML Element: <scm moniker>.repo-match}\label{sec:yaml-moniker-repo-match}
A regex applied to the source repository.  If the webhook payload has
a clone URL that matches the regex, this service definition is used to orchestrate scanning
for the received event.  As of \cxoneflow 2.1.0, this element will no longer allow regular
expressions such as \texttt{.*} that match any arbitrary value.  It is suggested to use
a regular expression that uses the start position anchor (\^{}) along with an expression
that matches the URL of the SCM that will be expected to emit the event.  The ending of
the expression can be followed by \texttt{.*} to match events from any repository.

This has been changed in consideration of secure deployment practices.  Please refer to
Appendix \ref{sec:cxoneflow-security} for more information.

\subsubsection{YAML Element: <scm moniker>.scan-config}\label{sec:yaml-moniker-scan-config}
A block element where the child elements define the default scan configuration for this service endpoint.

\subsubsection{YAML Element: <scm moniker>.service-name}\label{sec:yaml-moniker-service-name}
A moniker for the service definition. The moniker is used for logging and workflow purposes.







